### 2021-04-08 notes/notes.tex
End of day. Adaptation visualization complete.

\subsection{Left-right with unknown standard deviation (LRS)}
In this model, the force at each trial is assumed to be sampled from a normal
distribution and the mean of this distribution is inferred from the
observations, while the standard deviation is assumed to be known. The mean of
the force is assumed to also be normal with unknown mean and standard
deviation:
\begin{align}
  p(\gamma) &= N(\mu_t, \sigma) \\
  p(\mu_t) &= N(\mu_mu, \sigma_\mu)
\end{align}
In this manner, the uncertainty for this agent is at the level of the estimate
of the parameters of the force field, as opposed to being directly on the
force. Because the priors for $\mu_\mu$ are normal and the standard deviation
$\sigma$ (not $\sigma_mu$) is known, the update equations are given by:
\begin{align}
  \mu_\mu &= \frac{\sigma^2}{\sigma^2 + \sigma_\mu^2}\mu_\mu + \frac{\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2} x \\
  \sigma_\mu &= \frac{\sigma^2\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2}
\end{align}
where $x$ is the observation.

@@

Back to the lazy encoding of forces in the model, one can calculate the effects
of these forces on the arm. With a force of 10N and a $\Delta t$ of 50ms, the
total distance the arm will be moved by the force (again, assuming mass of 1Kg)
is given by:
\begin{align}
  d_\plusminus &= \plusminus \frac{1}{2}(\force / 1Kg)((\dt)^2)\\
               &= \plusminus 0.0125m
\end{align}
The agent will try to estimate $d_\plusminus$ during the experiment.

>>>>

\subsection{Left-right with unknown mean (LRS)}
In this model, the force at each trial is assumed to be sampled from a normal
distribution and the mean of this distribution is inferred from the
observations, while the standard deviation is assumed to be known. The mean of
the force is assumed to also be normal with unknown mean and standard
deviation:
\begin{align}
  p(\gamma) &= N(\mu_t, \sigma) \\
  p(\mu_t) &= N(\mu_mu, \sigma_\mu)
\end{align}
In this manner, the uncertainty for this agent is at the level of the estimate
of the parameters of the force field, as opposed to being directly on the
force. Because the priors for $\mu_\mu$ are normal and the standard deviation
$\sigma$ (not $\sigma_mu$) is known, the update equations are given by:
\begin{align}
  \mu_\mu &= \frac{\sigma^2}{\sigma^2 + \sigma_\mu^2}\mu_\mu + \frac{\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2} x \\
  \sigma_\mu &= \frac{\sigma^2\sigma_\mu^2}{\sigma^2 + \sigma_\mu^2}
\end{align}
where $x$ is the observation.

@@

Back to the lazy encoding of forces in the model, one can calculate the effects
of these forces on the arm. With a force of 10N and a $\Delta t$ of 50ms, the
total distance the arm will be moved by the force (again, assuming mass of 1Kg)
is given by:
\begin{align}
  d_\pm &= \pm \frac{1}{2}(\force / 1Kg)((\dt)^2)\\
               &= \pm 0.0125m
\end{align}
The agent will try to estimate $d_\pm$ during the experiment.
